General linear Models Coursework

### 2022-11-19 Draft_final.Rmd
Creating table for CI of sex and household

>>>>

```{r,echo=F}
#Creating table for effect of sex and household size
sum.final.model <- summary(lm.final.model)

#Vector of point estimate of household size
house.size.effect <- c(0,
                       sum.final.model$coefficients[9,1],
                       sum.final.model$coefficients[10,1],
                       sum.final.model$coefficients[11,1],
                       sum.final.model$coefficients[12,1])
#Vector of point estimate of effect of household size and female interaction
house.size.int <- c(0,
                       sum.final.model$coefficients[14,1],
                       sum.final.model$coefficients[15,1],
                       sum.final.model$coefficients[16,1],
                       sum.final.model$coefficients[17,1])
#vecotr of standard error of household size
house.size.effect.std <- c(0,
                       sum.final.model$coefficients[9,2],
                       sum.final.model$coefficients[10,2],
                       sum.final.model$coefficients[11,2],
                       sum.final.model$coefficients[12,2])
#vector of standard error of interation of household size and female
house.size.int.std <- c(0,
                       sum.final.model$coefficients[14,2],
                       sum.final.model$coefficients[15,2],
                       sum.final.model$coefficients[16,2],
                       sum.final.model$coefficients[17,2])
#lower and upper 95% CI bound for household size
house.size.lwr <- house.size.effect-1.96*house.size.effect.std
house.size.upr <- house.size.effect+1.96*house.size.effect.std
#lower and upper 95% CI bound for household and female interaction
house.size.int.lwr <- house.size.int-1.96*house.size.int.std
house.size.int.upr <- house.size.int+1.96*house.size.int.std

#lower and upper CI bound for being female and of household size [i]
female.house.lwr <- house.size.lwr+house.size.int.lwr+(sum.final.model$coefficients[13,1]-1.96*sum.final.model$coefficients[13,2])
female.house.upr <- house.size.upr+house.size.int.upr+(sum.final.model$coefficients[13,1]+1.96*sum.final.model$coefficients[13,2])

#Creating vector of 95% CI for male and female household head with [ith] household size
male.CI <- paste0("(",round(exp(house.size.lwr),3), ", ",round(exp(house.size.upr),3),")")
female.CI <- paste0("(",round(exp(female.house.lwr),3), ", ",round(exp(female.house.upr),3),")")

data.sex.household.CI <- data.frame(t(data.frame("Male"=male.CI, "Female"=female.CI)))%>%
  rename("1 Person"="X1",
         "2 Persons"="X2",
         "3 Persons"="X3",
         "4 Persons"="X4",
         "5+ Persons"="X5")

#creating table of 95% CI calculated
knitr::kable(data.sex.household.CI,digits=3,caption = "95% CI compared to male headed household of 1 person")%>%
  row_spec(0,bold=T)%>%
  column_spec(1,bold=T)%>%
  kable_styling(position = "center",latex_options = "HOLD_position")
```
